\documentclass[a4paper]{report}

\title{Foreign Exchange Management System (FXMS)}
\author{
    Yazeed AlKhalaf \\
    Mohammed Bin Jebreen \\
    Nawaf AlAmer \\
    \textbf{Course:} SWE 301 - Requirements Engineering \\
    \textbf{Instructor:} Dr. Noureddine Abbadeni
}
\date{19 Feb, 2024}

\begin{document}

\maketitle

\newpage

\chapter{}

\section{System Request}

\subsection{Project Sponsor}
Dr. Noureddine Abbadeni

\subsection{Business Need}
The need for a project like the Foreign Exchange Management System (FXMS) is crucial for businesses operating internationally for several reasons:
\begin{itemize}
    \item Operating internationally: Businesses engaged in importing and exporting goods and services will need a system like FXMS for currency conversion, enabling them to exchange their local currency for that of the country in which they wish to operate, thereby settling international transactions.
    \item Managing cash flow: Businesses operating overseas need to manage their cash across multiple currencies. FXMS will help them monitor and optimize their cash by converting currency at favorable rates and timings.
    \item Softening the risk: FXMS will provide businesses with tools to manage and mitigate the risks associated with fluctuations in currency prices. By using specific strategies, companies can lower the risk of exchange rate volatility and protect their profit margins.
\end{itemize}

\subsection{Business Value}
The Foreign Exchange Management System (FXMS) is expected to deliver some gains:
\begin{itemize}
    \item Quicker and Better Decision Making: Taking good decisions in a quick manner gives a competitive advantage in the international markets.
    \item Less Human Error: The human factor will be limited to things that require humans interaction and not things that are repetitive that are error prone.
    \item More Money: The amount of money traded will be more giving the organization a better chance at making more money.
\end{itemize}

\subsection{Business Requirements}
The functionality that the system should have includes:
\begin{itemize}
    \item Ability to manage clients and accounts (insert, update, delete).
    \item Ability to manage trades (insert, update, and delete trades). Any trader can enter new trades while updating and deleting existing trades require specific privileges.
    \item Ability to manage traders and coverage groups by assigning a trader to a coverage group, moving a trader from one coverage group to another.
    \item Ability to manage currencies and rates including daily updates of rates available in the market. The system is assumed to be connected with another system (such as Tadawul) which provides daily updates for exchange rates between all currencies.
\end{itemize}

\subsection{Constraints}
\begin{itemize}
    \item The system should run on Windows 10.
    \item The system should be delivered by the end of the year.
    \item Security must be considered during development.
\end{itemize}

\section{Feasibility Study}

\section{Methodology}

\section{Project Workplan}

\end{document}
